Hire Ed: Job Market Dynamics for Tenure-Track Faculty Positions in Archaeology

### 2025-05-23 analysis/paper/article.qmd
Git suggests I must commit before pulling so I am doing what it tells me.

The desire to pursue an academic career also characterizes more recent PhD cohorts, including those within archaeology. Brami et al's survey found that despite the long odds and grueling precaraity, 71% of their early career respondents wished to remain in academia [=@bramiPrecariousFutureReflections2023, pp. 242]. Overall, the obsessive valorization of permanent faculty positions in the face of a precipitous decline in available jobs is indicative of the potent combination of denial and delusion inacross academia. As Cefkin and Schwegler argue "This asymmetry between the “ideal” career path and the experiences of most graduates highlights the deep and growing chasm between the future that higher education institutions envision—and strongly incentivize—and what is actually happening" [@cefkin].

>>>>

The desire to pursue an academic career also characterizes more recent PhD cohorts, including those within archaeology. Brami et al's survey found that despite the long odds and grueling precaraity, 71% of their early career respondents wished to remain in academia [= @bramiPrecariousFutureReflections2023, pp. 242]. Overall, the obsessive valorization of permanent faculty positions in the face of a precipitous decline in available jobs is indicative of the potent combination of denial and delusion inacross academia. As Cefkin and Schwegler argue "This asymmetry between the “ideal” career path and the experiences of most graduates highlights the deep and growing chasm between the future that higher education institutions envision—and strongly incentivize—and what is actually happening" [@cefkin].
